### 2021-04-26 sections/languages.tex
Update languages.tex

\cvsection{Languages \& Softwares}

@@

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (fluent reading skills), French (elemental}

\cvskill
{} 
{reading skills)} \\

\cvskill
{Programming} 
{R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}

\cvskill
{} 
{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css},}

\cvskill
{} 
{{\scshape xhtml}, Notepad{\footnotesize ++}} \\

>>>>

\cvsection{Languages \& Software}

@@

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), French}

\cvskill
{} 
{(elemental reading skills)} \\

\cvskill
{Programming \&} 
{R, Python, Stata, {\scshape spss/pspp}, {\scshape ucinet}, NetDraw, RSiena, Gephi, Tosmana, Fuzzy-Sets, ArcGIS,}

\cvskill
{Software} 
{{\scshape atlas}.ti, EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html},}

\cvskill
{} 
{{\scshape css}, {\scshape xhtml}} \\
